\documentclass[11pt]{article}
\usepackage[margin=65pt]{geometry}

\title{\vspace{-80pt}\underline{Charlie Street: CV}}
\date{}

\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\begin{center}
		\vspace*{-40pt}
		\large7 Cassiobury Road,\\
		\large Weymouth,\\
		\large Dorset.\\
		\large DT4 7JN.\\	
		\large Phone: 07917601977\\
                     \large Email: charlie.street1@btinternet.com \\
	\end{center}

	
	
	\hspace{-100pt}\section*{\underline{Education}}
		\paragraph{}
			Harriott's talents also lay in comedy and singing as well as cooking and Harriott formed the Calypso Twins with schoolfriend Paul Boross, releasing a hit record in the early 1990s, "World Party". The Calypso Twins went on to be regular performers at the Comedy Store and Jongleurs; they also performed in America and on TV and radio shows. Harriott became head chef at Lord's Cricket Ground's Long Room. He was asked to present More Nosh, Less Dosh on BBC Radio 5 Live,[1] and also has appeared as an extra in Hale and Pace.[2]
	\vspace{-5pt}
	\hspace{-100pt}\section*{\underline{Languages}}
		\subsection*{Java:}
			\paragraph{}
				This is my most comfortable language. I have knowledge in the core of Java as well as graphics, interfaces, databases, lambda expressions, networking and web programming.

		\subsection*{Haskell:}
			\paragraph{}
			Although I have had less experience with this language, I have really warmed well to the functional paradigm since it allows me to easily write clean and concise code to carry out tasks which would take significantly longer to write in an imperative language such as java (e.g quicksort!)

	\vspace{-5pt}
	\hspace{-100pt}\section*{\underline{Soft Skills}}
		\begin{itemize}
			\item 2nd Year Computer Science Representative.
			\item I have taught a lesson on the use of the tkinter library to create menu driven interfaces in Python.
			\item As evidence for an ability to work well as a team, I have completed all 3 levels of the DOfE Award Scheme. This included a large amount of teamwork and communication during the expedition but soft skills have also been gained through the voluntary work involved in which I have been involved in voluntary work at a charity shop and also the restoration of a canal in the Cotswolds.
		\end{itemize}
	


\end{document}
