\documentclass[11pt]{article}
\usepackage[margin=65pt]{geometry}

\title{\vspace{-80pt}\underline{Charlie Street}}
\date{}
\hyphenation{Programme}%lets me remove hypenation for specific words
\hyphenation{Computer}
\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\vspace*{-60pt}
	\begin{flushright}
		\noindent
		\large7 Cassiobury Road, Weymouth ,Dorset. DT4 7JN\\                             
		\large 07917601977\\
          		 \large charlie.street1@btinternet.com
	\end{flushright}
	

	\vspace{-15pt}
	\begin{center}
			\textit{\large As a highly driven individual with a strong academic record, I throw myself into any challenge I am confronted with. With extra-curricular experience working in teams, I believe I can add value to any team-based project.}
	\end{center}
			
	\vspace{-30pt}
	\hspace{-100pt}\section*{\underline{Education}}
		\begin {itemize}
			\item \textbf{University (2014-2018)} Studying MSci Computer Science at the University of Birmingham.
				\begin{itemize}
					\item Achieved an average grade of\textbf{ 94\%} in first year with marks \textgreater 94\% in 6 modules.
					\item Won Best in Degree Programme 2014/15
					\item Won BCS Prize for Best in Year 2014/15
					\item Awarded School of Computer Science Excellence Scholarship
					\item Studying the second year modules of Computational Vision, Computer Security and C/C++
				\end{itemize}
			\item \textbf{A Level (2012-2014)} Studied at the Thomas Hardye Sixth Form, Dorchester, DT1 2ET.
				\begin{itemize}
					\item Achieved an A* in A Level Maths, Physics and Computing. I also achieved an A grade in AS Further Maths and Chemistry.
				\end{itemize}
			
			\item \textbf{GCSE Level (2007-2012)}  Studied at the Wey Valley School, Weymouth, DT3 5AN. 
				\begin{itemize}
					\item Achieved 9 GCSE's, 1 at A* grade, 1 at Distinction grade, 6 at A grade and 1 at B grade.
				\end{itemize} 
		\end{itemize}
	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Technical Skills}}
		\subsection*{\underline{Programming Languages}}
		\begin{itemize}
			\item \textbf{Java} I have a strong level of proficiency, having used it for multiple projects in the past year.
			\item \textbf{Haskell} Although I'm still learning Haskell, Ialready have a reasonable knowledge of it.
			\item \textbf{OCaml} I have an understanding of the syntax and underlying concepts of the language.
			\item \textbf{Python} I have familiarity with this language, as well as the Tkinter library for GUI's. 
			\item \textbf{JavaScript} I possess basic knowledge of the language to add functionality to webpages.
		\end{itemize} 
		\subsection*{\underline{Web Technologies}}
		\begin{itemize}
			\item \textbf{HTML, CSS, XML} I have enough knowledge of these to build basic webpages..
		\end{itemize}
		\subsection*{\underline{Other}}
		\begin{itemize}
			\item \textbf{(Postgre)SQL} I have the competence to define database entities and then query them
			\item \textbf{Git} I have experience using git, having used it for any significant projects I have partaken in.
		\end{itemize}

	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Extra-Curricular Interests And Experiences/Employment}}
			\begin{itemize}
				\item \textbf{Music} Outside of Computer Science, I am an avid musician, having played guitar for the past 7 years (both electric and acoustic). I have shown a lot of commitment to the instrument over the years,  and, for the past year, I have been a member of a band, providing lead guitar and backing vocals, with which I have performed with on occasion at local venues. Being a musician has benefitted my ability to persevere, particularly when learning difficult pieces. In particular, being an active member of a band has improved my ability to cooperate well within a group, specifically the ability to listen to the others around me. 
				\item \textbf{Teaching a lesson at my sixth form} During summer 2015 I was contacted by my A level Computing teacher, asking me to give a lesson to the current A2 students in order to aid their upcoming projects. I jumped upon the oppurtunity to do such and I gave the lesson in September 2015. The lesson subject was the use of the Tkinter library in Python to create menu driven interfaces. This was a great chance to develop my ability to communcate my ideas effectively.
				\item \textbf{Animal} Worked as a sales assistant in the Dorchester Store from November 2013 - September 2014, December 2014 - January 2015 and July 2015 - September 2015. Working in a retail environment has given me a large amount of experience working within a fairly small team of people. I feel such a job has also enhanced my communication skills, particularly when dealing with members of the public. 
				\item \textbf{DOfE Award} Over the last 5 years I have worked towards, and recently completed, all 3 levels of the DOfE award scheme. Doing this has consisted of large amounts of team-work and communication, particularly on the expedition section, involving working in a team of 4 for 4 days straight on Dartmoor. Such expeditions have also allowed me the chance to lead a team in terms of diection/morale. The scheme also gave me the oppurtunity to partake in voluntary work, having worked in a local charity shop as well as aiding restoration work along a canal near Stroud, Gloucestershire.
				\item \textbf{Cooking} Alongside my GCSE education, I also took a vocational NVQ course at my local college, giving me experience working in a functioning kitchen as well as working front of house in the college restaurant, both serving the public on a regular basis. Even after finishing the course, I still get enjoyment from it at home.
			\end{itemize}
				
	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{References}}	
				Professor Peter Tino:  P.Tino@cs.bham.ac.uk  \\
				University of Birmingham,\\
				Birmingham, 
				West Midlands.
				B15 2TT.\\
				Phone: (+44) (0)121 414 8558\\
				


\end{document}
