\documentclass[11pt]{article}
\usepackage[margin=65pt]{geometry}

\title{\vspace{-80pt}\underline{Charlie Street: CV}}
\date{}
\hyphenation{Programme}%lets me remove hypenation for specific words
\hyphenation{Computer}
\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\begin{center}
		\vspace*{-40pt}
		\large7 Cassiobury Road,\\
		\large Weymouth,\\
		\large Dorset.\\
		\large DT4 7JN.\\	
		\large Phone: 07917601977\\
                     \large Email: charlie.street1@btinternet.com \\
	\end{center}

	\vspace{7pt}
	\begin{center}
			\textit{\large As a highly driven individual with a strong academic record, I throw myself into any challenge I am confronted with. With extra-curricular experience working in teams, I believe I can add value to any team-based project; this lends wells to the industry of Computer Science.}
	\end{center}
			
	
	\hspace{-100pt}\section*{\underline{Education}}
		\begin {itemize}
			\item \textbf{University (2014-):} Studying at the University of Birmingham, West Midlands, B15 2TT.
				\begin{itemize}
					\item Achieved an average grade of 93.8\% for my first year.
					\item I am currently a second year student studying the four year MSci Computer Science Programme. I have chosen to take the optional modules of Computational Vision, Computer Security and C/C++ this current year. During my first year at 							university I was also awarded the 'School Of Computer Science Excellence Scholarship' which was awarded to me in light of academic record and an interview and aptitude test carried out on an applicant visit day.
				\end{itemize}
			\item \textbf{A Level (2012-2014):} Studied at the Thomas Hardye Sixth Form, Dorchester, Dorset, DT1 2ET.
				\begin{itemize}
					\item Achieved an A* in A Level Maths, Physics and Computing. I also achieved an A grade in AS Further Maths and Chemistry.
				\end{itemize}
			
			\item \textbf{GCSE Level (2007-2012):}  Studied at the Wey Valley School, Weymouth, Dorset, DT3 5AN. 
				\begin{itemize}
					\item Achieved 9 GCSE's, 1 at A* grade, 1 at Distinction grade, 6 at A grade and 1 at B grade.
				\end{itemize} 
		\end{itemize}
	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Technical Skills}}
		\subsection*{\underline{Programming Languages}}
		\begin{itemize}
			\item \textbf{Java:} A language that has given me a solid foundation and good understanding in Object Oriented paradigm. The largest code base I have contirbuted to in Java was for a localising and route following robot in the Robot Programming module.
			\item \textbf{Haskell:} A  language, which, alongside previous knowledge of OCaml has shown me the usefulness of the functional mindset and the elegance/conciseness it can provide compared to languages such as Java.
			\item \textbf{Python:}A self-taught language, I have familiarity with the basic syntax for Object Oriented Programming as well as the use of the Tkinter library to build GUI driven applications (such as an electronic sixth form application system for my A level computing project).
			\item \textbf{JavaScript:} A language I gained experience in as part of a module taken in first year. This was used alongside HTML and CSS to create a functional web page using Ajax based around the Premier League.
		\end{itemize} 
		\subsection*{\underline{Other languages}}
		\begin{itemize}
			\item \textbf{HTML, CSS and XML:} All 3 of these languages were learned as part of the Information And The Web module in first year and I have learned and praticed the languages through that.
			\item \textbf{(Postgre)SQL:} A language I am still in the process of learning, but one which has given me the ability to work with relational databases. I have experience with JDBC allowing me to write programs which communicate with databases on a server.
		\end{itemize}

	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Extra-Curricular Interests And Experiences/Employment}}
			\begin{itemize}
				\item \textbf{Music:} Outside of Computer Science, I am an avid musician, having played guitar for the past 7 years (both electric and acoustic). I have shown a lot of commitment to the instrument over the years,  and, for the past year, I have been a member of a band, providing lead guitar and backing vocals, with which I have performed with on occasion at local venues. Being a musician has benefitted my ability to persevere, particularly when learning difficult pieces. In particular, being an active member of a band has improved my ability to cooperate well within a group, specifically the ability to listen to the others around me. 
				\item \textbf{Teaching a lesson at my sixth form:} During summer 2015 I was contacted by my A level Computing teacher, asking me to give a lesson to the current A2 students in order to aid their upcoming projects. I jumped upon the oppurtunity to do such and I gave the lesson in September 2015. The lesson subject was the use of the Tkinter library in Python to create menu driven interfaces. This was a great chance to develop my ability to communcate my ideas effectively.
				\item \textbf{Animal:} Worked as a sales assistant in the Dorchester Store from November 2013 - September 2014, December 2014 - January 2015 and July 2015 - September 2015. Working in a retail environment has given me a large amount of experience working within a fairly small team of people. I feel such a job has also enhanced my communication skills, particularly when dealing with members of the public. 
				\item \textbf{DOfE Award:} Over the last 5 years I have worked towards, and recently completed, all 3 levels of the DOfE award scheme. Doing this has consisted of large amounts of team-work and communication, particularly on the expedition section, involving working in a team of 4 for 4 days straight on Dartmoor. Such expeditions have also allowed me the chance to lead a team in terms of diection/morale. The scheme also gave me the oppurtunity to partake in voluntary work, having worked in a local charity shop as well as aiding restoration work along a canal near Stroud, Gloucestershire.
				\item \textbf{Cooking:} Alongside my GCSE education, I also took a vocational NVQ course at my local college, giving me experience working in a functioning kitchen as well as working front of house in the college restaurant, both serving the public on a regular basis. Even after finishing the course, I still get enjoyment from it at home.
			\end{itemize}
				
	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{References}}	
				Peter Tino (Personal Tutor):  P.Tino@cs.bham.ac.uk  \\
				University Of Birmingham,\\
				Birmingham, 
				West Midlands.
				B15 2TT.\\
				Phone: (+44) (0)121 414 8558\\
				


\end{document}
