\documentclass[11pt]{article}
\usepackage[margin=65pt]{geometry}

\title{\vspace{-80pt}\underline{Charlie Street: CV}}
\date{}
\hyphenation{Programme}%lets me remove hypenation for specific words
\hyphenation{Computer}
\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\begin{center}
		\vspace*{-40pt}
		\large7 Cassiobury Road,\\
		\large Weymouth,\\
		\large Dorset.\\
		\large DT4 7JN.\\	
		\large Phone: 07917601977\\
                     \large Email: charlie.street1@btinternet.com \\
	\end{center}

	\vspace{7pt}
	\begin{center}
			\textit{\large As a highly driven individual with a strong academic record, I throw myself into any challenge I am confronted with. With extra-curricular experience working in teams, I believe I can add value to any team-based project; this lends wells to the industry of Computer Science.}
	\end{center}
			
	
	\hspace{-100pt}\section*{\underline{Education}}
		\begin {itemize}
			\item \textbf{GCSE Level:}  Studied at the Wey Valley School, Weymouth, Dorset, DT3 5AN. 
				\begin{itemize}
					\item Achieved 9 GCSE's, 1 at A* grade, 1 at Distinction grade, 6 at A grade and 1 at B grade.
				\end{itemize} 
			\item \textbf{A Level:} Studied at the Thomas Hardye Sixth Form, Dorchester, Dorset, DT1 2ET.
				\begin{itemize}
					\item A Level Maths at A* grade.
					\item A Level Physics at A* grade.
					\item A Level Computing at A* grade.
					\item AS Further Maths at A grade.
					\item AS Chemistry at A grade.
				\end{itemize}
			\item \textbf{University:} Studying at the University of Birmingham, Birmingham, West Midlands, B15 2TT.
				\begin{itemize}
					\item Achieved an average grade of 93.8\% for my first year.
					\item I am currently a second year student studying the four year MSci Computer Science Programme. I have chosen to take the optional modules of Computational Vision, Computer Security and C/C++ this current year. During my first year at university I was also awarded the 'School Of Computer Science Excellence Scholarship' which was awarded to me in light of academic record and an interview and aptitude test carried out on an applicant visit day.
				\end{itemize}
		\end{itemize}
	\vspace{-3pt}
	\hspace{-100pt}\section*{\underline{Programming Languages}}
		During my time studying Computer Science, I have had the oppurtunity to gain experience in multiple programming languages, giving me the diversity to choose when I am approaching a problem. These languages include:
		\begin{itemize}
			\item \textbf{Java:} A language that has given me a solid foundation and good understanding in Object Oriented paradigm.
			\item \textbf{Haskell}: A recently learnt language, which, alongside a small knowledge of OCaml has shown me the usefulness of the functional mindset and the elegance/conciseness it can provide compared to languages such as Java.
			\item \textbf{Python}: I have some self-taught but not extenisve knowledge of this language. I have used this language to built GUI driven applications such as an electronic sixth form application system for my A level computing project.
			\item \textbf{HTML and CSS}: I have a small knowledge base of these two languages, learnt as part of the Information and the Web module taken in my first year.
			\item \textbf{JavaScript}: Similar to HTML and CSS, I have some knowledge of JavaScript from taking the Information and the Web module in my first year.
		\end{itemize} 

	\vspace{-5pt}
	\hspace{-100pt}\section*{\underline{Employment History:}}
		\begin{itemize}
			\item \textbf{Animal:} Worked as a sales assistant in the Dorchester Store from November 2013 - September 2014, December 2014 - January 2015 and July 2015 - September 2015. Working in a retail environment has given me a large amount of experience working within a fairly small team of people.. I feel such a job has also improved my communication skills, particularly when dealing with members of the public. 
		\end{itemize}

	\vspace{-3pt}
	\hspace{-100pt}\section*{\underline{Extra-Curricular Interests And Experiences}}
			\begin{itemize}
				\item \textbf{Teaching a lesson at my sixth form:} During summer 2015 I was asked by my A level Computing teacher to give a lesson to the current A2 students in order to aid their upcoming projects. The lesson I gave was given in September 2015 and was on the use of the Tkinter library in Python to create menu driven interfaces; I learnt Python originally a few years ago for the purpose of aiding my project.
				\item \textbf{Music:} Outside of Computer Science, I am an avid musician, having played guitar for the past 7 years (both electric and acoustic), and, for the past year, I have been a member of a band, providing lead guitar and backing vocals, with which I have performed with on occasion at local venues. Being a musician has benefitted my ability to persevere, particularly when learning difficult pieces. In particular, being an active member of a band has improved my ability to cooperate well within a group. 
				\item \textbf{DOfE Award:} Over the last 5 years I have worked towards, and recently completed, all 3 levels of the DOfE award scheme. Doing this has involved consisted of large amounts of team-work and communication, particularly on the expedition section, involving working in a team of 4 for 4 days straight on Dartmoor. The scheme also gave me the oppurtunity to partake in voluntary work, having worked in a local charity shop as well as aiding restoration work along a canal near Stroud, Gloucestershire.
				\item \textbf{Cooking:} Alongside my GCSE education, I also took a vocational NVQ course at my local college, giving me experience working in a functioning kitchen as well as working front of house in the college restaurant, both serving the public on a regular basis. Even after finishing the course, I still get enjoyment from it at home.
			\end{itemize}
				
	\vspace{-3pt}
	\hspace{-100pt}\section*{\underline{References}}
			\paragraph{}
				References availiable on request.
				


\end{document}
