\documentclass[11pt]{article}
\usepackage[margin=65pt]{geometry}
\usepackage{multicol}
\title{\vspace{-80pt}\underline{Charlie Street}}
\date{}
\hyphenation{Programme}%lets me remove hyphenation for specific words
\hyphenation{Computer}
\hyphenation{Programming}
\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\vspace*{-60pt}
	\begin{flushleft}
		\noindent
		\large7 Cassiobury Road, Weymouth, Dorset. DT4 7JN\\                             
		\large 07917601977\\
          		 \large charlie.street1@btinternet.com
	\end{flushleft}
	

	\vspace{-15pt}
	\begin{center}
			\textit{\large As a highly driven individual with a strong academic record, I throw myself into any challenge I am confronted with. With extra-curricular experience working in teams, I believe I can add value to any team-based project.}
	\end{center}
			
	\vspace{-30pt}
	\hspace{-100pt}\section*{\underline{Education}}
		\begin {itemize}
			\item \textbf{University (2014-2018)} Studying MSci Computer Science at the University of Birmingham.
				\begin{itemize}
					\item Achieved an average grade of\textbf{ 94\%} in first year with marks $\geq$ 94\% in 6 modules.
					\item Won Best in Degree Programme 2014/15.
					\item Won BCS Prize for Best in Year 2014/15.
					\item Awarded School of Computer Science Excellence Scholarship during first year.
					\item Studying the optional modules of Computational Vision, Computer Security and C/C++.
					\item I have already completed modules in Logic, Java Programming, Robot Programming, AI, Software Engineering and the Foundations of Computer Science.
				\end{itemize}
			\item \textbf{A Level (2012-2014)} Studied at the Thomas Hardye Sixth Form, Dorchester.
				\begin{itemize}
					\item Achieved an A* in A Level Maths, Physics and Computing. I also achieved an A grade in AS Further Maths and Chemistry.
				\end{itemize}
			
			\item \textbf{GCSE Level (2007-2012)}  Studied at the Wey Valley School, Weymouth.
				\begin{itemize}
					\item Achieved 9 GCSE's, 1 at A* grade, 1 at Distinction grade, 6 at A grade and 1 at B grade.
				\end{itemize} 
		\end{itemize}
	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Technical Skills}}
		\subsection*{\underline{Programming Languages}}
		\renewcommand{\arraystretch}{1.5}%
		\begin{tabular}[20pt]{ll}
			 \textbf{Java} &  I have a strong level of proficiency, having used Java for multiple projects in the past year.\\
			 \textbf{Haskell} & Although I'm still learning this language, I already have a reasonable knowledge of it.\\
			 \textbf{OCaml} & I have an understanding of the syntax and underlying concepts of the language.\\
			 \textbf{Python} & I have familiarity in using this language, as well as the Tkinter library for GUI's. \\
			\textbf{JavaScript} &  I possess basic knowledge of the language to add functionality to web-pages.\\
		\end{tabular} 
		\subsection*{\underline{Web Technologies}}
		\renewcommand{\arraystretch}{1.5}%
		\begin{tabular}{ll}
			\textbf{HTML, CSS, XML} & I have enough knowledge of these to build basic, functional web-pages.\\
		\end{tabular}
		\subsection*{\underline{Other}}
		\renewcommand{\arraystretch}{1.5}%
		\begin{tabular}{ll}
			\textbf{(Postgre)SQL} & I have the competency to define database entities and then query them.\\
			 \textbf{Git} & I have experience using git, having used it for any significant projects I have partaken in.\\
			\textbf{LaTeX} & I have enough knowledge to produce clear and well formatted documents.\\
			\textbf{Matlab} & I have a very simple understanding in utilising matrices and writing basic functions.\\
		\end{tabular}

	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Employment}}
			\begin{itemize}
				\item \textbf{Animal (clothing shop) }I worked as a sales assistant in the Dorchester Store from November 2013 - September 2014, December 2014 - January 2015 and July 2015 - September 2015. Working in retail has given me experience working within a fairly small team of people as well as enhancing my communication skills, particularly when dealing with members of the public. 
			\end{itemize}

	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Extra-Curricular Interests And Experiences/Employment}}
			\begin{itemize}
				\item \textbf{Duke Of Edinburgh Award} Over recent years I have completed all 3 levels of the Duke of Edinburgh award scheme. This has required large amounts of team-work and communication, particularly during expeditions, which involved working in a team of 4 for 4 days on Dartmoor. This has also greatly benefited my leadership skills. I also partook in voluntary work including working in a local charity shop and aiding restoration work along a canal near Gloucester.
				\item \textbf{Teaching a lesson at my sixth form} During summer 2015 I was contacted by an old computing teacher to give a lesson to the current A2 students to aid their upcoming projects. I gave the lesson in September 2015 and chose to talk about the basics of Object Oriented Programming, followed by a tutorial on using the Tkinter library in Python. This gave me a great chance to learn how to communicate my ideas effectively. 
				\item \textbf{Music} I am an avid musician, having played the guitar since I was 12 and having interest in multiple genres of music. This has required great commitment and perseverance. Additionally, for the past year, I have been a member of a rock covers band, providing lead guitar and backing vocals. Being an active member of a band has improved my ability to cooperate well within a group and to listen to those around me. 
				\item \textbf{Cooking} Alongside my GCSE education, I also took a vocational NVQ course in catering at my local college, giving me experience working in a functioning kitchen as well as working front of house in the college restaurant; both serve the public on a regular basis. Even after finishing the course, I still get enjoyment from it at home.
			\end{itemize}

	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Additional Information}}
		\begin{itemize}
			\item \textbf{BCS} I am currently a student member of the British Computer Society.
		\end{itemize}

				
	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{References}}	
				\begin{multicols}{2}
					\noindent
					Professor Peter Tino:  P.Tino@cs.bham.ac.uk  \\
					University of Birmingham,\\
					Birmingham, \\
					West Midlands.\\
					B15 2TT.\\
					(+44) (0)121 414 8558\\
	
					\noindent
					Dr. Mark Lee: m.g.lee@cs.bham.ac.uk\\
					University of Birmingham,\\
					Birmingham,\\
					West Midlands,\\
					B15 2TT.\\
					(+44) (0)121 414 4765\\
				\end{multicols}


\end{document}
