\documentclass[12pt]{article}
\usepackage[margin = 65pt]{geometry}

\begin{document}

	\pagenumbering{gobble}

	\begin{flushright}
		7 Cassiobury Road,\\
		Weymouth,\\
		Dorset.\\
		DT4 7JN.\\
                07917 601977\\
                charlie.street1@btinternet.com\\
                \hfill\break
                2nd November 2015
	\end{flushright}

	\begin{flushleft}
		University of Birmingham,\\
		Birmingham,\\
		West Midlands.\\
		B15 2TT.
	\end{flushleft}

	\begin{flushleft}
		Dear Dr. Mark Lee, 
		\paragraph{}
			I am writing to you to apply for the role of Software Developer advertised on your company's website as of the 30th October 2015. Please find attached with this letter my CV.
	
		\paragraph{}
			Having spent the last year gaining and developing new technical skills, in particular with the Java programming language, I am now looking to utilise these skills in a real working environment. This is what attracted me to your current vacancy for a Software Developer. Your company's previous use of machine learning concepts within commercial software interests me as this is an area I intend to pursue much further in the following years of my studies.

		\paragraph{}
			This role requires a strong proficiency in Java and I believe that I can satisfy this requirement. As well as the large amount of time I have spent using Java over the past year, I achieved 99\% in a module solely based upon the language. I hope this demonstrates my ability to write in Java to the professional standard you are looking for.

		\paragraph{}
			The advertised role also requires strong communication skills as well as the ability to participate well in teams and my CV shows this. As well as the extra curricular demonstrations of such skills, I have also engaged in other group-based projects during my studies. This includes a Robot Programming module based solely on group work, in which the team I was part of achieved a score of 100\%. This module also required to give a presentation explaining our work. One role in particular I took in the team was to ensure all of our code was clear and readable, such that any member of the team could understand each other's work.

		\paragraph{}
			The role of Software Developer would allow me to put my skills with Java into practice in an area that piques my interest. Thank you for taking the time to read this application and I look forward to discussing it with you in the future.\\

		
	\end{flushleft}
	\begin{flushleft}
		Yours sincerely,
		\newline
		\break
		Charlie Street
	\end{flushleft}

\end{document}
