\documentclass[12pt]{article}
\usepackage[margin = 65pt]{geometry}

\begin{document}

	\pagenumbering{gobble}

	\begin{flushright}
		7 Cassiobury Road,\\
		Weymouth,\\
		Dorset.\\
		DT4 7JN.
	\end{flushright}

	\begin{flushleft}
		University of Birmingham,\\
		Birmingham,\\
		West Midlands.\\
		B15 2TT.
	\end{flushleft}

	\begin{flushleft}
		Dear Dr. Mark Lee, 
		\paragraph{}
			I am writing to you to apply for the role of Software Developer as advertised on your company's website as of the 30th October 2015. Please find attached with this letter my CV.
	
		\paragraph{}
			Having spent the last year gaining and developing new technical skills, in particular with the Java programming language, I am now looking to utilise these skills in a real working environment. This is what attracted me to your current vacancy for a Software Developer. Your company's previous use of machine learning concepts within commercial software interests me as this is an area I intend to pursue much further in the following years of my studies.

		\paragraph{}
			This role requires a strong proficiency in Java and I believe that I can satisfy this requirement. As well as the large amount of time I have spent using Java over the past year, I achieved 99\% in a module solely based upon the language. I hope this demonstrates my ability to write in Java to the professional standard you are looking for.

		\paragraph{}
			The advertised role also requires strong communication skills as well as the ability to participate well in teams and my CV shows this. As well as the extra curricular demonstrations of such skills on my CV, I have also engaged in other group-based projects during my studies. This includes a Robot Programming module based solely on group work, in which the team I was part of achieved a score of 100\% for the module.

		\paragraph{}
			As I hope my CV shows, I would be a valuable addition to your company. Thank you for taking the time to read this application and I look forward to discussing this application with you in the future.\\

		
	\end{flushleft}

	\begin{flushleft}
		Yours sincerely,
		\newline
		\break
		Charlie Street
	\end{flushleft}

\end{document}